Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-11 draft.tex
rewrite description of status quo payoffs as state variable

If both $s$ and $g$ play Status Quo, then the status quo persists. The status quo payoffs for the secessionists are modeled as steadily declining due to the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs from the status quo, in the absence of other actions, are given by $q_{s,t+1} = Q_{s,t} - \mu$. Lower case letters denote beginning-of-period quantities net of investments by outside actors, while upper case letters denote end-of-period quantities gross of such investments. Other payoffs remain unchanged from period to period; they can only be altered by the investments of players $p$ or $c$, e.g. $L_{s,t} = l_{s,t} + R_{p,t} + R_{c,t}$ and $l_{s,t+1} = L_{s,t}$, likewise for player $g$ and for the payoffs from winning for both players and the status quo for player $g$. %who can expend resources ($R$) to increase a payoff at the rate $\gamma$.  For example, if $p$ expends resources to aid the secessionists, the payoff $Q_s$ becomes $Q_s+\gamma R_p$ in the round that the resources are expended.

>>>>

If both $s$ and $g$ play Status Quo, then the status quo persists. The status quo payoffs for the secessionists are modeled as a state variable. The transition of this state variable from one period to the next involves an increase by the amount of the patron's investment and an automatic reduction by $\mu$.\footnote{Note that it is also possible for the international community to make an investment in the secessionists status quo payoffs, but we will show that they have no incentive to do so.} The steady reduction by $\mu$ represents the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs from the status quo, in the absence of other actions, are given by $q_{s,t+1} = Q_{s,t} - \mu$. Lower case letters denote beginning-of-period quantities net of investments by outside actors, while upper case letters denote end-of-period quantities gross of such investments.

Other payoffs are also modeled as state variables. However, they remain unchanged from period to period unless players $p$ or $c$ make an investment, e.g. $L_{s,t} = l_{s,t} + R_{p,t} + R_{c,t}$ and $l_{s,t+1} = L_{s,t}$, likewise for player $g$ and for the payoffs from winning for both players and the status quo for player $g$.
